\textls[-15]{\thetitle \mbox{(Technical Report)}}

### 2022-11-03 casestudies.tex
cite Types as AI

A second family, \lsti{ImpGAI}, extends \lsti{Imp} and contains
\textasciitilde 450~LOC.
It exports a generic framework for deriving provably sound
abstract interpreters.
The soundness theorem of this generic abstract interpreter, \lsti{analyze},
is with respect to the big-step interpreter, \lsti{eval}.
It states that the abstraction relation \lsti{RState} over a
concrete state~\lsti{S} and an abstract state~\lsti{absS} is preserved
by the analysis:

@@

The other two families then extend \lsti{ImpGAI}.
Family \lsti{ImpTyping} (\textasciitilde200~LOC) is an abstract
interpreter that does type inference.
Family \lsti{ImpCP} (\textasciitilde300~LOC) extends the abstract syntax
with natural number arithmetic via \lsti{FInductive},
and instantiates the generic abstract interpreter to perform constant propagation.
%
Gallina code generated for these two families are runnable;
they are put to test over simple queries.

>>>>

A second family, \lsti{ImpGAI}, extends \lsti{Imp} and contains
\textasciitilde 450~LOC.
It exports a generic framework for deriving provably sound
abstract interpreters.
The soundness theorem of this generic abstract interpreter, \lsti{analyze},
is with respect to the big-step interpreter, \lsti{eval}, inherited from \lsti{Imp}.
It states that the abstraction relation \lsti{RState} over a
concrete state~\lsti{S} and an abstract state~\lsti{absS} is preserved
by the analysis:

@@

The other two families then extend \lsti{ImpGAI}.
Family \lsti{ImpTyping} (\textasciitilde200~LOC) is an abstract
interpreter that does type inference~\cite{cousot1997types}.
Family \lsti{ImpCP} (\textasciitilde300~LOC) extends the abstract syntax
with natural number arithmetic,
and instantiates the generic abstract interpreter to perform constant propagation.
%
Gallina code generated for these two families are runnable;
they are put to test over simple queries.
